Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-03 jss/article.tex
[skip ci] jss update

@@

>>>>

The example shown below is the simplest command that can be done to test a gene
list for over-representation on the six included ACSN maps. With the list of 12
genes mentionned above and a default p-value cutoff of $0.05$, we have a set of
36 maps or modules that are significantly enriched. The results are structured
as a data frame with nine columns displaying the module name, the module size,
the number of genes from the list in the module, the names of the genes that are
present in the module, the size of the reference universe, the number of genes
from the list that are present in the universe, the raw p-value, the p-value
corrected for multiple testing and the type of test performed. The module field
in the results data frame indicate the map name and the module name separated by
a column character. If a complete map is significantly enriched or depleted,
then only the map name is shown, without any module or column character. For
instance, the first line of the results object below concern the E2F1 module of
the Apoptosis map.

@@

%    enrichment(Genes = NULL, maps = ACSNMineR::ACSN_maps,
%       correction_multitest = "BH", statistical_test = "fisher",
%       min_module_size = 5, universe = "map_defined", threshold = 0.05,
%       alternative = "greater")

The \code{enrichment} function can take up to eight arguments: the gene list (as
a character vector), the list of maps that will be used to calculate enrichment
or depletion, the type of statistical test (either the Fisher exact test or the
hypergeometric test), the module minimal size for which the calculations will be
done, the universe, the p-value threshold and the alternative ("greater" for
calculating over-representation, "less" for depletion and "both" for both
tests).

Only the gene list is mandatory to call the \code{enrichment} function, all the
other arguments have default values.
